\section{Design}
The application is made up of activities, retainable fragments, and different types of listeners. When starting the application, the first screen visible to the player is the main menu defined in \emph{MainActivity}. This activity contains the three buttons: `Play', `Instructions' and `Highscore'. The buttons navigate from the \emph{MainActivity} to the buttons' corresponding activities within the application. 

When the instruction button is tapped, \emph{InstructionsActivity} appears with a slideshow of images that explain the rules of the game. The user can navigate through the images by swiping left and right. \newline

When the play button is tapped, \emph{PhotoActivity} opens where the user has to choose a bonus card. This can either be a default card or a personal photo taken with the device’s default camera application. To be able to use this, the application uses the camera permission. \newline

After the user has made a choice, \emph{GameActivity} starts and the game begins. When the game is over, the user can go to the main menu or stay in \emph{GameActivity} to play again. If the player's score is high enough to make it into the highscore list, the player can submit the score and enter \emph{HighscoreActivity}. This activity is as previously mentioned also accessible from the main menu. \newline

To handle a part of the game logic, we have used a retainable fragment with an AsyncTask. This fragment is called VerifyFragment. It checks the type of interaction that the player has performed and whether the two images are identical or not. Another fragment used in the game is a  DialogFragment called \emph{FinishDialogFragment}, where the options change based on the player’s score. \newline

The buttons in \emph{PhotoActivity} are ImageViews with added OnClickListeners, while OnTouchListener is mainly used for the fling gesture in the game and the instructions menu. Within the OnTouchListener there is a custom gesture listener that makes it possible to have full control over the different types of gestures available in \emph{GameActivity} and in \emph{InstructionsActivity}.

